Tropopause Evolution in a Rapidly Intensifying Tropical Cyclone: A Static Stability Budget Analysis in an Idealized, Axisymmetric Framework

### 2018-02-21 paper.tex
Finished radiation section of Discussion and started turbulent mixing section.

  \subsection{The role of radiation}
During the initial spin-up period (0-24 hours; \ref{fig:qi+radten}a), convection was not deep enough to deposit large quantities of ice near the tropopause in the mean.
Due to the lack of ice particles, the radiative heating tendencies during this period (\ref{fig:qi+radten}b) were relatively small and confined to the region above a few particularly strong convective towers.
During RI (24-48 hours; \ref{fig:qu+radten}b), the eyewall updraft strengthened and a radially-extensive cirrus canopy developed near the tropopause.
The enhanced vertical gradient of ice mixing ratio at the top of the cirrus canopy induced strong diurnal-mean radiative cooling near the tropopause (\ref{fig:qi+radten}d).
This cooling exceeded 0.6 K h\textsuperscript{-1} in some places and sloped downward from the lower stratosphere into the upper troposphere, following the top of the cirrus canopy.
A small radiative warming maximum also appeared outside of the 140-km radius below this region of cooling.
These results broadly agree with those of \citeauthor{buetal} (\citeyear{buetal}; see their Fig. 11a), whose CM1 simulations 0.3 K net diurnally-averaged radiative cooling at the top of the cirrus canopy and radiative warming within the cloud maximized near the 200-km radius.
The broad region of radiative cooling acted to destabilize the layer below the cooling maximum and stabilize the layer above, which can be seen in Fig. \ref{fig:h024-048}d.
The small area of net radiative heating outside of the 140-km radius enhanced the destabilization in this region and produced a thin layer of stabilization in the 15-16-km layer.

At steady-state strong radiative cooling remained near the tropopause at inner radii, sloping downward with the top of the cirrus canopy to below the tropopause at outer radii.
Cooling rates exceeded 1 K h\textsuperscript{-1} just above the tropopause between the 30 and 70 km radii.
These cooling rates exceeded those observed by \cite{buetal}, a discrepancy that is likely a consequence of their larger vertical grid spacing (625 m) compared to that used here (250 m), with a possible a contribution from differing radiation schemes\footnote{\cite{buetal} employed the NASA-Goddard radiation scheme for their CM1 simulations, whereas RRTMG is used in the present paper. They did use the RRTMG radiation scheme alongside the Thompson microphysics parameterization for their HWRF simulations, but those simulations also produced smaller radiative tendencies than those seen here (see their Fig. 5a), suggesting that vertical resolution accounts for most of the difference in radiative heating rates.}

@@

Radiative heating and turbulence viscosity figures?

Discuss how turbulence increases the static stability in some regions --> vertical gradients of turblence intensity.

@@

Bu et al. did not see a lower-stratospheric inflow layer, likely due to their 625-m grid spacing. If we want to resolve properly the radiative cooling at the top of the cirrus canopy and the lower-stratospheric inflow layer, we must have sufficient vertical resolution in the tropopause layer. Our 100-m grid spacing here may not even be sufficient, given how shallow the layer is!

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% ACKNOWLEDGMENTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\acknowledgments
We are indebted to George Bryan for his continued development and support of Cloud Model 1.
We also thank Jeffrey Kepert, Robert Fovell, and Erika Navarro for helpful conversations related to this work.
ADD GRANT NUMBER

>>>>

  \subsection{The role of radiation}
During the initial spin-up period (0-24 hours; \ref{fig:qi+radten}a), convection was not deep enough to deposit large quantities of ice near the tropopause in the mean.
Due to the lack of ice particles, the radiative heating tendencies during this period (Fig. \ref{fig:qi+radten}b) were relatively small and confined to the region above a few particularly strong convective towers.
During RI (24-48 hours; Fig. \ref{fig:qi+radten}b), the eyewall updraft strengthened and a radially-extensive cirrus canopy developed near the tropopause.
The enhanced vertical gradient of ice mixing ratio at the top of the cirrus canopy induced strong diurnal-mean radiative cooling near the tropopause (\ref{fig:qi+radten}d).
This cooling exceeded 0.6 K h\textsuperscript{-1} in some places and sloped downward from the lower stratosphere into the upper troposphere, following the top of the cirrus canopy.
A small radiative warming maximum also appeared outside of the 140-km radius below this region of cooling.
These results broadly agree with those of \citeauthor{buetal} (\citeyear{buetal}; see their Fig. 11a), whose CM1 simulations 0.3 K net diurnally-averaged radiative cooling at the top of the cirrus canopy and radiative warming within the cloud maximized near the 200-km radius.
The broad region of radiative cooling acted to destabilize the layer below the cooling maximum and stabilize the layer above, which can be seen in Fig. \ref{fig:stab-24-48}d.
The small area of net radiative heating outside of the 140-km radius enhanced the destabilization in this region and produced a thin layer of stabilization in the 15-16-km layer.

After the TC's RI period completed (48-72 hours; Fig. \ref{fig:qi+radten}f), strong radiative cooling remained near the tropopause at inner radii, sloping downward with the top of the cirrus canopy to below the tropopause at outer radii.
Cooling rates exceeded 1 K h\textsuperscript{-1} just above the tropopause between the 30- and 70-km radii.
These cooling rates exceeded those observed by \cite{buetal}, a discrepancy that is likely a consequence of their larger vertical grid spacing (625 m) compared to that used here (250 m), with a possible a contribution from differing radiation schemes\footnote{\cite{buetal} employed the NASA-Goddard radiation scheme for their CM1 simulations, whereas RRTMG is used in the present paper. They did use the RRTMG radiation scheme alongside the Thompson microphysics parameterization for their HWRF simulations, but those simulations also produced smaller radiative tendencies than those seen here (see their Fig. 5a), suggesting that vertical resolution accounts for most of the difference in radiative heating rates.}.
Time-mean radiative warming spread from 30- to 160-km radius within the cirrus canopy.
The existence of radiative cooling overlying radiative warming in this region led to radiatively-forced destabilization at and below the tropopause, as was observed in Fig. \ref{fig:stab-48-72}d.
Below the warming layer existed a region of forcing for stabilization, while a much stronger region of forcing for destabilization existed above the cooling maximum in the lower stratosphere.

The results herein suggest that radiative heating tendencies played an important role in destabilizing the upper troposphere and stabilizing the lower stratosphere after the cirrus canopy developed and persisted during and after RI.

@@

Although vertical turbulence always acts to eliminate vertical gradients of $\theta$, this adjustment toward a neutral state only occurs where the mixing takes place.
If turbulence occurs in a stably-stratified layer, it will act to decrease $\theta$ at the top of the layer and increase it below.
Just above and just below the mixed layer, however, the $\theta$ profile remains undisturbed.
Consequently, although turbulent mixing acts to decrease $\partial \theta/\partial z$ in the layer in which it is occurring, it actually increases $\partial \theta/\partial z$ just below and just above the layer.
These vertical gradients of turbulent mixing are quite important, particularly on the flanks of the upper-tropospheric outflow jet.

@@

Bu et al. did not see a lower-stratospheric inflow layer, likely due to their 625-m grid spacing. If we want to resolve properly the radiative cooling at the top of the cirrus canopy and the lower-stratospheric inflow layer, we must have sufficient vertical resolution in the tropopause layer. Our 100-m grid spacing here may not even be sufficient, given how shallow the layer is!
Did my no-CRF simulation show a lower-stratospheric inflow layer?? If not, that's strong evidence supporting the role of radiation in producing the desceding inflow layer above the tropopause.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% ACKNOWLEDGMENTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\acknowledgments
We are indebted to George Bryan for his continued development and support of Cloud Model 1.
We also thank Jeffrey Kepert, Robert Fovell, and Erika Navarro for helpful conversations related to this work.
This research was supported by NSF Grant \#1636799.
